---
title: "Visualization"
subtitle: "Part I" 
output: github_document
---

```{r setup}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```


## Scatterplots
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

## new approach, same plot
```{r}
weather_df %>% # with this option, you can mutate, basically work with data and then plot.
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit plot object.
```{r}
weaather_plot =
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

weaather_plot + geom_point()
```


##Advanced scatterplot
Start with the same one and make it fancy:
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + #by adding the color = name you get some variation
  geom_point() + 
  geom_smooth(se = FALSE)
```


What about the aes placement? 
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

Let's facet some things!!
```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + #by adding the color = name you get some variation
  geom_point(alpha = .5, size = 0.8) + #alpha level is the transparency, 50% transparency  
  geom_smooth(se = FALSE) + 
  facet_grid(.~ name) #dot means nothing specifies rows, and name defines columns.
```


Let's combine some elements and try a new plot 
```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_grid(.~ name)
```

## Some small notes 
How many geoms have to exist?
You can have whatever geoms you want but this may not be a good idea..
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_smooth(se = FALSE)
```


You can use a neat geom 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_hex()
```

## Univariate plots

Histograms are really great 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) + 
  geom_histogram()
```

Can you add a color to a histogram? 
There are a couple of issues the color is behind the bar and the data isn't as appealing visually if you just use color = name.
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge") #instead of stacking, it dodges
```

Rather than worrying about positions, it may be easier to just use a facet grid
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram() + 
  facet_grid(. ~ name)
```

Let's try a new geometry (helps with comparing the shapes of the distributions)
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = 0.3) 
```

What about box plots? 
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot()
```

Trendy plots
```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) + 
  geom_violin(alpha = .5) + 
  stat_summary(fun = "median")
```

Ridge plots 
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) + 
  geom_density_ridges()
```


Saving plots 
```{r}
weather_plot = 
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))

ggsave("weather_plot.pdf")
```